6.890 Spring 2019 Project Proposal \\ LHYRA: Learned HYbrid Recursive Algorithms

### 2019-03-19 proposal/proposal.tex
tex typo fix

\begin{itemize}
	\item \textbf{Bag of solvers $S$.} Each solver $s_i \in S$ is equipped to solve an instance of the problem at hand, potentially by calling the LHYRA instance on subproblems. Each solver $s_i$ may also have a set of hyperparameters $h_ij$.

@@

\begin{enumerate}
	\item Compute $F(x)$.
	\item Pass $F(x)$ into the solver selector learned by the optimizer, which returns a parametrized solver $s_ih$.
	\item Compute $s_ih(x)$.
	\begin{enumerate}
		\item For each subproblem $y_i$ identified by $s_ih$, repeat the above process.
		\item Combine the subproblems and return a result.
	\end{enumerate}
\end{enumerate}

>>>>

\begin{itemize}
	\item \textbf{Bag of solvers $S$.} Each solver $s_i \in S$ is equipped to solve an instance of the problem at hand, potentially by calling the LHYRA instance on subproblems. Each solver $s_i$ may also have a set of hyperparameters $h_{ij}$.

@@

\begin{enumerate}
	\item Compute $F(x)$.
	\item Pass $F(x)$ into the solver selector learned by the optimizer, which returns a parametrized solver $s_{ih}$.
	\item Compute $s_{ih}(x)$.
	\begin{enumerate}
		\item For each subproblem $y_i$ identified by $s_{ih}$, repeat the above process.
		\item Combine the subproblems and return a result.
	\end{enumerate}
\end{enumerate}
